---
title: "data_viz_final"
output: html_document
date: "2023-04-22"
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.

```{r}
library(shiny)
library(dplyr)
library(ggplot2)
library(DT)

# Load data from CSV file
data <- read.csv("unicef_indicator_1.csv")

# Create a table of alpha_3_code using DT package
alpha3_table <- datatable(data %>% select(alpha_3_code) %>% unique())

# Define the UI for the Shiny app
ui <- fluidPage(
  # Search bar for alpha_3_code
  sidebarLayout(
    sidebarPanel(
      textInput("alpha3_search", "Enter alpha_3_code:")
    ),
    # Output plot
    mainPanel(
      plotOutput("scatterplot")
    )
  ),
  # Output table
  fluidRow(
    column(12, alpha3_table)
  )
)

# Define the server for the Shiny app
server <- function(input, output) {
  
  # Filter data based on input value from search bar
  filtered_data <- reactive({
    if (input$alpha3_search == "") {
      data
    } else {
      data %>% filter(alpha_3_code == input$alpha3_search)
    }
  })
  
  # Create scatterplot with linear regression line based on filtered data
  output$scatterplot <- renderPlot({
    ggplot(filtered_data(), aes(x = time_period, y = obs_value)) +
      geom_point() +
      geom_smooth(method = "lm", se = FALSE, color = "red") +
      labs(title = paste("Observed Values for Alpha_3_Code:", input$alpha3_search),
           x = "Time Period", y = "Observed Value")
  })
}

# Run the Shiny app
shinyApp(ui, server)

```

